On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-03-27 manuscripts/PNAS/chazthm_pnas.tex
SteamRoll page 1

\begin{abstract}
Dictionary learning methods for sparse linear coding have exposed underlying structure in many kinds of natural signals.
However, universal theorems guaranteeing the statistical consistency of inference in this model are lacking.
Here, we prove that for almost all diverse enough datasets generated from the sparse coding model, latent dictionaries and sparse codes are uniquely determined up to an error commensurate with measurement noise.
Applications are given to data analysis, neuroscience, and engineering.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

@@

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}. Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, which have found sparse representations to be a powerful tool for the manipulation of signals lacking much known analytic structure (see \cite{Zhang15} for a comprehensive review). This motivates the data-driven approach to inferring optimal dictionaries for a wide variety of signal classes for which, traditionally, representations have been constructed using methods of harmonic analysis (e.g., the Fourier basis, wavelets, curvelets, etc.). A popular formulation of the idea is to find a set of $m$ `elementary' waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$. 
%\dropcap{D}ictionary learning methods for sparse coding have been under active development ever since their application to natural images brought about an exciting discovery in computational neuroscience: that simple-cell response properties emerge from efficient coding principles \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}. Much of the subsequent work in dictionary learning has come out of the signal processing and machine learning communities, whose interest in sparse representations as a practical tool motivates the data-driven approach to inferring optimal dictionaries (see \cite{Zhang15} for a comprehensive review). A popular formulation of the idea is to find a set of $m$ `elementary' signals, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.

Blind source identification first started \cite{sato1975method}.

We address here a question of fundamental concern to this enterprise: \emph{When are dictionaries and the sparse representations they provide uniquely determined by data?} An affirmative answer speaks also to the important question of whether or not a dictionary adapted to a finite number of samples from a signal class will generalize in its ability to represent all signals in the class; see, for instance, the method of forgery detection by analysis of local painting style proposed in \cite{hughes2010, Olshausen10}. Fortunately, algorithms with proven recovery of generating dictionaries under certain conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art). It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
%[**TODO** make sure the claim here is right...or would it be punchier to talk about the fact that everyone always gets Gabors on natural images?]
%- algos with proven recovery of generating dictionary
%- analyses of when target dictionary is local optimizer of natural recovery criteria
%- efficient algos that globally solve DR; detailed models differ but all assume each col has bounded sparsity and nonzero coefs have sub-Gaussian magnitudes

The main finding of this work is that for any $k < m$, every dictionary satisfying the spark condition \eqref{SparkCondition} from compressed sensing is identifiable from as few as $N = m + m(k-1){m \choose k}$ $k$-sparse linear combinations of its elements up to an error linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}). In fact, provided $(n, m, k)$ satisfy the nearly-optimal compressed sensing inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}). Interestingly, these guarantees hold even without constraining the recovered matrix to satisfy the spark condition. Imposing this constraint does, however, allow us to state a modification of our main result that applies to the case where only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}). We hope the explicit, algorithm-independent criteria we provide here may serve as a useful tool in future analyses of dictionary learning procedures.

We state the problem considered here more precisely as follows. Fix a dictionary represented as the columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) of a matrix $\mathbf{A} \in \mathbb R^{n \times m}$ and suppose a dataset $Z$ consists of measurements:
\begin{align}\label{LinearModel}
\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\indent \text{$i=1,\ldots,N$},
\end{align}
for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.

@@

Note that by formulating the problem in this way we have introduced the following ambiguity. Any particular solution represents a whole class of equivalent dictionaries $BPD$ and codes $D^{-1}P^{\top}\mathbf{\hat x}_i$, where $P$ is any permutation matrix and $D$ any invertible diagonal matrix. We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}. Alternatively, one may seek a unique solution (in the usual sense) in the quotient space induced by the action of the transformation group of matrices $PD$.

Previous work \cite{li2004analysis, Georgiev05, Aharon06, Hillar15} on the noiseless case $\eta = 0$ has shown that the solution (when it exists) is indeed unique in the sense described above provided the $\mathbf{x}_i$ are sufficiently diverse and the matrix $\mathbf{A}$ satisfies the \textit{spark condition}:
\begin{align}\label{SparkCondition}
\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2,\indent \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2.
\end{align}
%
which would be, in any case, a necessary condition for uniqueness if we knew only that the $\mathbf{x}_i$ are $k$-sparse. We introduce the following terminology to handle $\eta > 0$. 
\begin{definition}
Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$. We say $Y$ has a \emph{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$. %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively. 
This representation is \emph{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy
\begin{align*}
\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon \ \ \text{for all $i$}
\end{align*}
%
then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
\begin{align}\label{def1}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 \leq \delta_2.
\end{align}
\end{definition}
% Kato mentions a distance between n-tuples that minimizes the maximum difference over all possible orderings of one of the n-tuples.
% Make just 'sparse representation in m-dimensions? (i.e. with k unspecified?)

We ask here: \emph{When does $Y$ have a stable $k$-sparse representation in $m$ dimensions?} To see how an answer to this question informs the interpretation of solutions to Problem \ref{InverseProblem}, suppose that \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in recovery \eqref{def1}. Consider now any dataset $Z$ generated as in \eqref{LinearModel} that has $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$. Then, any dictionary $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Problem \ref{InverseProblem} are necessarily close to the original matrix $\mathbf{A}$ and codes $\mathbf{x}_i$ (i.e., satisfy \eqref{def1}). Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.

In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$. We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} while stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}). Our proof is a refinement of the arguments in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. All other proofs are relegated to the Supplemental. Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.

@@

In fact, the spark condition can be made explicit.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for all the $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
\begin{align*}
f(\mathbf{A}) = \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
\end{align*}
%
where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.

@@

@@

\textbf{Theoretical Neuroscience}.
Sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons. Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations. Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).   
%TODO: add reproduction of response propeties in olfactory cortex?

>>>>

\begin{abstract}
Dictionary learning for sparse linear coding has exposed underlying structure in many natural signals.
However, there are few universal theorems guaranteeing uniqueness of model estimation independent of implementation.
Here, we prove that for all diverse enough datasets generated from the sparse coding model, latent dictionaries and codes are uniquely determined up to measurement error.  Applications are given to data analysis, neuroscience, and engineering. 
\end{abstract}

% \dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

@@

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{B}lind source identification is a classical problem in signal processing \cite{sato1975method}.  
One popular modern formulation of the idea is to find a dictionary of $m$ elementary waveforms, at most $k$ of which need be linearly combined to represent each $n$-dimensional signal in a dataset of size $N$, typically where $k < m \ll N$.  Approximating solutions to this problem have
provided insight into the structure of many signals lacking explicit analytic structure (see \cite{Zhang15} for a comprehensive review). 
In particular, it has been shown that response properties of simple-cell neurons in mammalian visual cortex emerge from learning a dictionary for sparse linear coding of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent}, a major advance in computational neuroscience. A fundamental aspect of this finding is that the latent waveforms (``Gabors'') estimated from data appear to be canonical; i.e., they are found in learned dictionaries independent of algorithmic implementation or natural image training set.

% (e.g., Fourier bases, wavelets, etc.)

Motivated by these discoveries and earlier work in the theory of neural communication \cite{Coulter10, Isely10}, we address when dictionaries and sparse representations are uniquely determined by data.  Answers to this question also have other real-world implications.  For example, a sparse coding analysis of local painting style can be used for forgery detection \cite{hughes2010, Olshausen10}, but only if sparse components of the artwork are independent of implementation idiosyncrasies. Fortunately, algorithms with proven recovery of generating dictionaries under certain 
conditions have recently been proposed (see \cite[Sec.~I-E]{Sun16} for a summary of the state-of-the-art).  However,
there are few general theorems explaining the general phenomenon of uniqueness.

Here, we prove very generally that uniqueness in sparse linear coding is an expected property of the model.  In other words, whenever enough sparsely represented data generated from a dictionary (satisfying a spark condition) are observed, the original codes and dictionary are uniquely determined up to an error that is commensurate with the measurement noise.  Applications of this result include:  (1) a sufficient diversity of sparse codes sent through a random linear compressive channel are unique, (2) the sparse linear coding problem is well-posed in the sense of Hadamard \cite{Hadamard1902}, and (3) an explanation for universal representation of natural signals in neuroscience.

% It has remained unknown, however, when the dictionary learning problem is well-posed (as per Hadamard \cite{Hadamard1902}) in general -- that is, independent of all methodological idiosyncracies.
%[**TODO** make sure the claim here is right...or would it be punchier to talk about the fact that everyone always gets Gabors on natural images?]
%- algos with proven recovery of generating dictionary
%- analyses of when target dictionary is local optimizer of natural recovery criteria
%- efficient algos that globally solve DR; detailed models differ but all assume each col has bounded sparsity and nonzero coefs have sub-Gaussian magnitudes

More formally, let $\mathbf{A} \in \mathbb R^{n \times m}$ be a matrix with columns $\mathbf{A}_j$ ($j = 1,\ldots,m$) and let dataset $Z$ consist of measurements:
\begin{align}\label{LinearModel}
\mathbf{z}_i = \mathbf{A}\mathbf{x}_i + \mathbf{n}_i,\indent \text{$i=1,\ldots,N$},
\end{align}
for $k$-\emph{sparse} $\mathbf{x}_i \in \mathbb{R}^m$ having at most $k$ nonzero entries and \emph{noise} $\mathbf{n}_i \in \mathbb{R}^n$, with bounded norm $\| \mathbf{n}_i \|_2 \leq  \eta$ representing our combined worst-case uncertainty in  measuring $\mathbf{A}\mathbf{x}_i$.
The precise mathematical problem addressed here is the following.
% We address the uniqueness properties for the following linear coding question in signal processing.

@@

Note that any particular solution $(\mathbf{B}, \mathbf{\hat x}_1 \ldots, \mathbf{\hat x}_N)$ to this problem gives rise to an orbit of other solutions $(\mathbf{BPD}, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_1 \ldots, \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_N)$, where $\mathbf{P}$ is any permutation matrix and $\mathbf{D}$ any invertible diagonal.  
We therefore consider whether solutions to Problem~\ref{InverseProblem} are unique only up to this ambiguity.  More specifically, 
we seek conditions for when sparsely coded datasets have a stable unique representation.

% More specifically,  we seek sufficient conditions on when sparsely coded datasets have a stable unique representation.

% We therefore consider only whether solutions to Problem~\ref{InverseProblem} are unique up to this equivalence \cite{Li15}

% Note that by formulating the problem in this way we have introduced the following ambiguity. Any particular solution represents . Alternatively, one may seek a unique solution (in the usual sense) in the quotient space induced by the action of the transformation group of matrices $PD$.

%  noiseless case $\eta = 0$

%  We introduce the following terminology to handle $\eta > 0$. 
\begin{definition}\label{maindef}
Fix $Y = \{ \mathbf{y}_1, \ldots, \mathbf{y}_N\} \subset \mathbb{R}^n$. We say $Y$ has a \textbf{$k$-sparse representation in $m$ dimensions} if there exists a matrix $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$ such that $\mathbf{y}_i = \mathbf{A}\mathbf{x}_i$ for all $i$. %Equivalently, $\mathbf{Y} = \mathbf{A}\mathbf{X}$ for $\mathbf{Y}$ and $\mathbf{X}$ having the $\mathbf{y}_i$ and $\mathbf{x}_i$ as their columns, respectively. 
This representation is \textbf{stable} if for every $\delta_1, \delta_2 \geq 0$, there exists $\varepsilon = \varepsilon(\delta_1, \delta_2) \geq 0$ (with $\varepsilon > 0$ when  $\delta_1, \delta_2 > 0$) such that if a matrix $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N \in \mathbb{R}^m$ satisfy:
\begin{align*}
\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\hat x}_i\|_2 \leq \varepsilon, \ \ \text{for all $i$},
\end{align*}
%
then there is some permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ such that for all $i, j$:
\begin{align}\label{def1}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq \delta_1 \ \ \text{and} \ \ \|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\hat x}_i\|_1 \leq \delta_2.
\end{align}
\end{definition}
% Kato mentions a distance between n-tuples that minimizes the maximum difference over all possible orderings of one of the n-tuples.
% Make just 'sparse representation in m-dimensions? (i.e. with k unspecified?)

To see how Definition \ref{maindef} directly relates to Problem \ref{InverseProblem}, suppose that $Y$
% \mbox{$Y = \{\mathbf{A} \mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$} 
has a stable $k$-sparse representation in $m$ dimensions and fix $\delta_1, \delta_2$ to be the desired accuracy in \eqref{def1}. Consider now any dataset $Z$ generated as in \eqref{LinearModel} with $\eta \leq \frac{1}{2} \varepsilon(\delta_1, \delta_2)$. Then, any dictionary $\mathbf{B}$ and $k$-sparse $\mathbf{\hat x}_1, \ldots, \mathbf{\hat x}_N$ solving Problem \ref{InverseProblem} are necessarily close to the original matrix $\mathbf{A}$ and codes $\mathbf{x}_i$ (i.e., satisfy \eqref{def1}).

%Our results, outlined in Sec.~\ref{Results}, include an explicit form for $\varepsilon(\delta_1, \delta_2)$ in Thm.~\ref{DeterministicUniquenessTheorem}.

% We ask here: \emph{When does $Y$ have a stable $k$-sparse representation?}

Previous theoretical work on Problem \ref{InverseProblem} for the noiseless case $\eta =0$ (e.g., \cite{li2004analysis, Georgiev05, Aharon06, Hillar15}) has shown that a solution (when it exists) is indeed unique provided the $\mathbf{x}_i$ are sufficiently diverse and the generating matrix $\mathbf{A}$ satisfies the \textit{spark condition} from compressed sensing (CS):
\begin{align}\label{SparkCondition}
\mathbf{A}\mathbf{x}_1 = \mathbf{A}\mathbf{x}_2 \implies \mathbf{x}_1 = \mathbf{x}_2, \ \ \ \text{for all $k$-sparse } \mathbf{x}_1, \mathbf{x}_2,
\end{align}
%
which would be, in any case, a necessary condition for uniqueness if it were known only that $\mathbf{x}_i$ are $k$-sparse.

Our main technical finding is that a sufficient diversity of measurements generated from any dictionary satisfying the spark condition 
has a stable sparse representation.  More specifically, such dictionaries are uniquely identifiable from as few as \mbox{$N = m + m(k-1){m \choose k}$} sparse linear combinations of its columns up to an error that is linear in the measurement noise (Thm.~\ref{DeterministicUniquenessTheorem}). In fact, provided $(n, m, k)$ satisfy the CS inequality \eqref{CScondition}, in almost all cases the dictionary learning problem is well-posed given enough data (Cor.~\ref{ProbabilisticCor}). Importantly, these guarantees hold without assuming the recovered matrix satisfies the spark condition. Our results  also apply when only an upper bound on the number of dictionary elements is known (Thm.~\ref{DeterministicUniquenessTheorem2}). We hope the explicit, algorithm-independent criteria we provide here are useful tools in future analyses of dictionary learning.

In the next section, we give precise statements of our main results, which include an explicit form for $\varepsilon(\delta_1, \delta_2)$. We then prove our main theorem (Thm.~\ref{DeterministicUniquenessTheorem}) in Sec.~\ref{DUT} while stating some additional definitions and lemmas required for the proof, including our main tool from combinatorial matrix analysis (Lem.~\ref{MainLemma}). All other proofs are relegated to the Supplemental. Our approach is a refinement of the one found in \cite{Hillar15} to handle noise and to reduce the sufficient number of samples.
%for all $k < m$ from $N=k{m \choose k}^2$ to $N = m + m(k-1){m \choose k}$. 
Finally, several applications are considered in our discussion, Sec.~\ref{Discussion}.

@@

In fact, the spark condition can be made explicit.  Let $\mathbf{A}$  be the $n \times m$ matrix of $nm$ indeterminates $A_{ij}$. When real numbers are substituted for all the $A_{ij}$, the resulting matrix satisfies \eqref{SparkCondition} if and only if the following polynomial is nonzero:
\begin{align*}
f(\mathbf{A}) := \prod_{S \in {[m] \choose k}} \sum_{S' \in {[n] \choose k}} (\det \mathbf{A}_{S',S})^2,
\end{align*}
%
where for any $S' \in {[n] \choose k}$ and $S \in {[m] \choose k}$, the symbol $\mathbf{A}_{S',S}$ denotes the submatrix of entries $A_{ij}$ with $(i,j) \in S' \times S$.   We note that the large number of terms in this product is likely necessary due to the NP-hardness of deciding whether $A$ satisfies a given spark condition \cite{tillmann2014computational}.

@@

Phrased 
in the language of Hadamard \cite{Hadamard1902}),

@@

\textbf{Theoretical Neuroscience}.
Sparse dictionary learning and related methods have recovered characteristic components of natural images \cite{Olshausen96, hurri1996image, bell1997independent, van1998independent} and sounds \cite{bellsejnowski1996, smithlewicki2006, Carlson12}, reproducing response properties of cortical neurons. Our theorems suggest that this correspondence could be due to the uniqueness of sparse representations. Furthermore, our guarantees justify the hypothesis of \cite{Coulter10} and \cite{Isely10} that sparse codes passed through a communication bottleneck in the brain can be recovered from random projections via (unsupervised) biologically plausible sparse dictionary learning (e.g., \cite{rehnsommer2007, rozell2007neurally, hu2014hebbian}).

Invariance in neuroscience: Pitts \cite{pitts1947}.
%TODO: add reproduction of response propeties in olfactory cortex?
